### 2011-09-16 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress

TODO compare this to pure GLPK run - for example for 100-200, we got from TODO seconds to on average 1.3 seconds.

@@

Second: if we don't have enough time, we should do XYZ but it might depend on the characteristics of the data.
For realistic (looks like THIS in graph representation) it is best to do A B C.
Whereas, for artificial data (having IJK as their representation) it is best to just do 1 2 3.

>>>>

TODO compare this to pure GLPK run - for example for \dataset{100-1000}, we got from TODO (90+ on average) seconds to on average TODO seconds (when the 10 second limit is lifted).

TODO this will need 2 boxplots again...

@@

Second: if we don't have enough time, we should do Strategy 1. In under 10 seconds we will have very good results (often the optimum).

% TODO if possible, write down in lessons learned:
% - always allow for interruptions
% - in experiments, iterations should be the outermost loop
% - when representing an object, don't be lazy and create a class for it (don't use pairs, lists with specific data at specific locations, etc)
